{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-10 thesis/landslide.tex
minor changes landslide

Traversal of the state space is implemented in three parts:
first, identifying preemption points when first encountered and selecting which thread to run for its first execution, in {\tt arbiter.c},
second, selecting which preemption point to backtrack to after completing an execution
and which thread to ``have switched to''
\footnote{\revision{willan on-having switched to \cite{hhgg-reu}}}
instead, in {\tt explore.c},
and third, rewinding the machine state to implement said backtracking,
in {\tt timetravel.c} (Bochs version) and {\tt timetravel-simics.c} (Simics version).

@@

First of all, note that \Cref{alg:icb} is structured in a way that repeats interleavings
with fewer than $n$ preemptions that have already been checked in previous iterations of the outer loop.
This is because the number of preemptions in each branch is not known in advance;
rather, the state space must always be explored in an overall depth-first approach,
at best skipping too-preemptful interleavings as they are encountered.
As simple as it would be to state ``{\bf foreach} $S \in {\mathsf{sort}_P(U)}$'' in pseudocode,
implementing such an ordering would be much less straightforward.
\footnote{\revision{The pseudocode algorithms found in many conference papers
often fail to be straightforward to translate into usable implementations~\cite[Figure 5]{itg2}.}}

@@

\begin{itemize}
	\item Extends Preemption Sealing for finer-grained control
		over whether individual functions and/or global variables
		should be considered for, or excluded from,
		DPOR and/or data-race analysis
		(\cref{sec:landslide-config-landslide};
		{\tt thrlib\_function} and {\tt ignore\_dr\_function}, respectively).
		This allows a test case author to precisely target the exact subset of code
		she is interested in testing,
		avoiding unnecessary state space inflation from trusted code.
	\item Adds a mutex testing mode to configure whether the
		data race analysis should consider lock' internal accesses
		(\cref{sec:landslide-dynamicconfig}; {\tt TESTING\_MUTEXES}).
		This allows the user to verify that her lock implementation
		correctly provides mutual exclusion
		(upcoming in \cref{sec:education-pebbles-tests}; {\tt mutex\_test}),
		before relying on them as trusted code in subsequent tests.
	\item Implements the sleep set extension to DPOR \cite{partial-order-methods,dpor,optimal-dpor},
		which identifies and skips further equivalences based on which memory accesses
		DPOR intended to reorder,
		%, rather than just switching threads and seeing what happens
		in a way that is slightly less optimal compared to prior work,
		but much simpler to implement
		and requires less state at runtime (\cref{sec:landslide-sleepsets}).
	\item Heuristically identifies infinite loops and livelocks
		by leveraging knowledge of how long the test program should be expected to run
		obtained during previous executions,
		uniquely suited to stateless model checking (\cref{sec:landslide-infloop}).
	\item Provides automatic code instrumentation facilities,
		beyond just the simple task of identifying important function boundaries,
		that attempt to understand a wide variety of even the most unusual student implementations
		(\cref{sec:landslide-pebblesspecifics},
		\cref{sec:landslide-pintosspecifics}).
		This includes an advanced heuristic for detecting ad-hoc synchronization loops
		that Landslide should treat as blocking, %a thread,
		even if it does not trigger the automatically-inserted blocking annotations
		(\cref{sec:landslide-blocking-yield}),
		and a further heuristic to ensure that any inaccuracy on the part of the first heuristic
		does not result in false-positive bug reports (\cref{sec:landslide-fp-deadlock}).
\end{itemize}

>>>>

Traversal of the state space is implemented in three parts:
first, identifying preemption points when first encountered and selecting which thread to run for its first execution, in {\tt arbiter.c},
second, selecting which preemption point to backtrack to after completing an execution
and which thread to ``have switched to''
\footnote{\revisionminor{willan on-having switched to \cite{hhgg-reu}}}
instead, in {\tt explore.c},
and third, rewinding the machine state to implement said backtracking,
in {\tt timetravel.c} (Bochs version) and {\tt timetravel-simics.c} (Simics version).

@@

First of all, note that \Cref{alg:icb} is structured in a way that repeats interleavings
with fewer than $n$ preemptions that have already been checked in previous iterations of the outer loop.
This is because the number of preemptions in each branch is not known in advance;
rather, the state space must always be explored in an overall depth-first approach,
at best skipping too-preemptful interleavings as they are encountered.
As simple as it would be to state ``{\bf foreach} $S \in {\mathsf{sort}_P(U)}$'' in pseudocode,
implementing such an ordering would be much less straightforward.
\footnote{\revisionminor{The pseudocode algorithms found in many conference papers
often fail to be straightforward to translate into usable implementations~\cite[Figure 5]{itg2}.}}

@@

\begin{itemize}
	\item Extends Preemption Sealing for finer-grained control
		over whether individual functions and/or global variables
		should be considered for, or excluded from,
		DPOR and/or data-race analysis
		(\cref{sec:landslide-config-landslide};
		{\tt thrlib\_function} and {\tt ignore\_dr\_function}, respectively).
		This allows a test case author to precisely target the exact subset of code
		she is interested in testing,
		avoiding unnecessary state space inflation from trusted code.
	\item Adds a mutex testing mode to configure whether the
		data race analysis should consider locks' internal accesses
		(\cref{sec:landslide-dynamicconfig}; {\tt TESTING\_MUTEXES}).
		This allows the user to verify that her lock implementation
		correctly provides mutual exclusion
		(upcoming in \cref{sec:education-pebbles-tests}; {\tt mutex\_test}),
		before relying on them as trusted code in subsequent tests.
	\item Implements the sleep set extension to DPOR \cite{partial-order-methods,dpor,optimal-dpor},
		which identifies and skips further equivalences based on which memory accesses
		DPOR intended to reorder,
		%, rather than just switching threads and seeing what happens
		in a way that is slightly less optimal compared to prior work,
		but much simpler to implement
		and requires less state at runtime (\cref{sec:landslide-sleepsets}).
	\item Heuristically identifies infinite loops and livelocks
		by leveraging knowledge of how long the test program should be expected to run
		obtained during previous executions,
		uniquely suited to stateless model checking (\cref{sec:landslide-infloop}).
	\item Provides automatic code instrumentation facilities,
		beyond just the simple task of identifying important function boundaries,
		that attempt to understand a wide variety of even the most unusual student implementations
		(\cref{sec:landslide-pebblesspecifics},
		\cref{sec:landslide-pintosspecifics}).
		This includes an advanced heuristic for detecting ad-hoc synchronization loops
		that Landslide should treat as blocking, %a thread,
		even if it does not trigger the automatically-inserted blocking annotations
		(\cref{sec:landslide-blocking-yield}),
		and a further heuristic to ensure that any inaccuracy on the part of the first heuristic
		does not result in false-positive bug reports (\cref{sec:landslide-fp-deadlock}).
\end{itemize}
